% ============================================================
% COREY 论文 LaTeX 修改建议（NeurIPS Reviewer 风格）
% 所有 patch 均可直接复制替换对应位置
% ============================================================


% ============================================================
% PATCH 1：重写 Contributions 段（必须）
% 位置：main.tex，\paragraph{Contributions.} 整段
% 原因：当前 contribution 表述过于模糊，reviewer 无法判断
%       哪些是理论贡献、哪些是系统贡献、哪些是实验贡献
% ============================================================

% ------- 替换前 -------
% Contributions. (1) We introduce an entropy-driven criterion ...
% (2) We design a fused Hadamard layer ...
% (3) We connect entropy gain with outlier suppression ...
% (4) We validate ...

% ------- 替换后（直接复制）-------
\paragraph{Contributions.}
This paper makes the following concrete contributions,
each at a clearly defined scope:

\begin{itemize}

\item \textbf{Entropy-guided fusion metric (systems design).}
We introduce a runtime scheduling score
$S(\mathcal{R}) = \alpha\widetilde{H}(\mathcal{R})
  + \beta\widetilde{AI}(\mathcal{R})
  - \gamma\widetilde{M}(\mathcal{R})$
that integrates normalized activation entropy, arithmetic
intensity, and memory-traffic estimates into a unified
fusion-boundary criterion.
Unlike static kernel graphs or heuristic depth limits,
this signal adapts to prompt-dependent activation
statistics at inference time.

\item \textbf{Fused Hadamard reparameterization (algorithm).}
We show that a normalized Hadamard matrix can be absorbed
into adjacent linear projections ($W' = WH^\top$) while
preserving exact functional equivalence.
Theorem~\ref{thm:quant} provides a quantitative
$\sqrt{d}$-factor bound on peak-coordinate contraction,
directly relevant to clipping-limited low-bit execution.

\item \textbf{Two-tier evaluation methodology (empirical).}
We design a prototype-to-checkpoint validation pipeline
that separates (i) a deterministic cost-model study
isolating entropy and scheduling signals (Tier~1) from
(ii) real-GPU feasibility measurements on public
Mamba-370M and Mamba-1.4B checkpoints (Tier~2).
This separation prevents prototype assumptions from
contaminating deployment-facing claims.

\item \textbf{Distribution-gap characterization (empirical observation).}
We demonstrate that the entropy-increase property of
Theorem~\ref{thm:entropy} holds in the synthetic
heavy-tailed regime (34/35 instances, Sinkhorn $\ell_1$
residual $0.070\pm0.010$) but does \emph{not} transfer
to real Mamba in\_proj activations (entropy decreases
in all 80 real (layer, sample) pairs,
$\ell_1$ residual $1.689\pm0.037$).
This gap is reported not as a failure but as an
actionable finding for future distribution-aware
scheduling design.

\end{itemize}


% ============================================================
% PATCH 2：将三个定理改为正式 amsthm 环境（强烈建议）
% 位置：main.tex preamble（\begin{document} 之前）和 Section 4
% 原因：用 \paragraph 声明定理不符合 NeurIPS 规范，
%       reviewer 看到会直接扣分
% ============================================================

% ------- 在 preamble 中添加（\begin{document} 之前）-------
\usepackage{amsthm}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{remark}[theorem]{Remark}
\newtheorem{corollary}[theorem]{Corollary}

% ------- Section 4.1 替换前 -------
% \paragraph{Theorem 1 (Entropy Increase ...)}

% ------- Section 4.1 替换后 -------
\begin{theorem}[Entropy Increase Under Doubly-Stochastic
Histogram Mixing]
\label{thm:entropy}
Let $p \in \Delta^m$ be the empirical histogram mass
vector of activations before rotation, and let
$q \in \Delta^m$ be the histogram mass vector after
rotation using the same fixed bins.
If there exists a doubly-stochastic matrix
$B \in \mathbb{R}^{m \times m}$ such that $q = Bp$,
then $H_{\mathrm{hist}}(q) \ge H_{\mathrm{hist}}(p)$.
If $B$ is not a permutation and $p$ is non-uniform,
the inequality is strict.
\end{theorem}

\begin{remark}[Conditional applicability]
\label{rem:conditional}
Theorem~\ref{thm:entropy} is conditional: it requires
the post-rotation histogram to be representable as a
doubly-stochastic mixing of the pre-rotation histogram
over the same fixed bins.
In the synthetic heavy-tailed prototype regime
(35~instances), this condition holds with Sinkhorn
$\ell_1$ residual $0.070 \pm 0.010$~(34/35 below~0.10).
In real Mamba checkpoint activations
(mamba-370m, layers~0--3, 80~(layer,sample) pairs),
entropy \emph{decreases} in all cases
(mean gain $-1.30 \pm 0.47$ nats,
$\ell_1$ residual $1.689 \pm 0.037$),
indicating that the doubly-stochastic condition does
not hold for near-Gaussian in\_proj outputs.
The theorem therefore motivates using the entropy
signal in the synthetic calibration regime, not as
an unconditional guarantee on real checkpoints.
\end{remark}

% ------- Section 4.2 替换前 -------
% \paragraph{Theorem 2 (Shared-Memory Depth Bound).}

% ------- Section 4.2 替换后 -------
\begin{theorem}[Shared-Memory Depth Bound]
\label{thm:depth}
Let $M_{\mathrm{shared}}$ denote the available shared
memory per thread block, and let $C_{\mathrm{tile}}$
denote the incremental memory footprint contributed by
each additional fused operator under a fixed tile shape.
Then the fusion depth $F$ must satisfy
\[
  F \;\le\; \frac{M_{\mathrm{shared}}}{C_{\mathrm{tile}}}.
\]
In practice, the prototype scheduler tracks
per-operator costs $C_i$ and enforces
$\sum_{i=1}^{F} C_i \le M_{\mathrm{shared}}$;
the homogeneous form above exposes the first-order
depth limit transparently.
\end{theorem}

% ------- Section 4.3 替换前 -------
% \paragraph{Theorem 3 (Variance Preservation ...)}

% ------- Section 4.3 替换后 -------
\begin{theorem}[Variance Preservation with Reduced
Coordinate Extremes]
\label{thm:quant}
Let $H \in \mathbb{R}^{d \times d}$ be a normalized
Hadamard matrix and let $z = Hx$.
Then total variance is preserved,
$\|z\|_2 = \|x\|_2$,
and the peak coordinate obeys
\[
  \|z\|_\infty \;\le\; \frac{\|x\|_1}{\sqrt{d}}.
\]
Consequently, for any clipping threshold $T > 0$,
\[
  \Pr\!\bigl(\|z\|_\infty > T\bigr)
  \;\le\;
  \Pr\!\Bigl(\|x\|_1 > T\sqrt{d}\Bigr).
\]
In the one-outlier regime $x = M e_r$,
the peak magnitude is reduced from $M$ to exactly
$M/\!\sqrt{d}$.
\end{theorem}


% ============================================================
% PATCH 3：在 Section 5.3 末尾添加超参数说明（必须）
% 位置：main.tex，\subsection{Quantization and Kernel
%        Configuration} 末尾
% 原因：reviewer 必问 hand-tuned 问题；
%       目前说明分散，需集中交代
% ============================================================

% ------- 在该小节末尾追加 -------
\paragraph{Hyperparameter status.}
The fusion weights $(\alpha,\beta,\gamma) =
(0.45, 0.35, 0.20)$ and default threshold
$\tau = 0.52$ are hand-tuned prototype defaults
rather than the result of a systematic search.
The present revision supports them with
(i)~a $\tau$-sweep over $\{0.45, 0.52, 0.60\}$,
(ii)~a coarse $3\times3$ grid over
$\alpha \in \{0, 0.45, 0.90\}$ and
$\beta \in \{0, 0.35, 0.70\}$ with $\gamma$
fixed at~0.20 (Table~\ref{tab:ablation_alpha_beta}),
and (iii)~matched-depth arithmetic-only ablations that
isolate the entropy term's contribution.
A full joint search over $(\alpha,\beta,\gamma)$ remains
future work.
The key finding from the coarse grid is that neither
entropy alone ($\alpha=0.45,\beta=0$, depth~$\approx1.1$)
nor arithmetic intensity alone ($\alpha=0,\beta=0.70$,
depth~$2.33$) achieves the fusion depth or latency
reduction of the combined default
($\alpha=0.45,\beta=0.35$, depth~$3.15$--$3.50$),
confirming that the entropy term provides independent
discriminative power.


% ============================================================
% PATCH 4：补充 ablation 总结表（审稿人必问）
% 位置：main.tex Section 7（Ablation Studies）开头
% 原因：ablation 结论目前只在附录，主文缺汇总；
%       reviewer 不应该翻附录才能看到核心消融结果
% ============================================================

% ------- 替换前 -------
% All five prototype ablation studies ... are reported in
% Appendix A.9.

% ------- 替换后 -------
Table~\ref{tab:ablation_summary} summarises the key
findings across the five prototype ablation axes.
Full per-bucket traces are in Appendix~A.9; all values
are Tier-1 surrogate timings from the deterministic
Python cost model and should not be read as GPU hardware
measurements.

\begin{table}[t]
\centering
\caption{%
  Ablation summary across five axes (FP16 prototype,
  ultra-long bucket unless noted).
  All latency values are Tier-1 surrogate timings.
  ``Depth'' is mean fusion group depth.
  Lower latency and lower diagnostic proxy are better.}
\label{tab:ablation_summary}
\begin{tabular}{llccc}
\toprule
Axis & Configuration
  & Depth & Latency (ms)$\downarrow$
  & Diag.\ Proxy$\downarrow$ \\
\midrule
\multirow{4}{*}{Score weights}
  & No signal ($\alpha{=}\beta{=}0$)
    & 1.00 & 100.94 & -- \\
  & Arith.-only ($\alpha{=}0,\beta{=}0.70$)
    & 2.33 & 83.79  & -- \\
  & Entropy-only ($\alpha{=}0.45,\beta{=}0$)
    & 1.08 & 99.07  & -- \\
  & \textbf{Default} ($\alpha{=}0.45,\beta{=}0.35$)
    & \textbf{3.50} & \textbf{77.97} & \textbf{0.000} \\
\midrule
\multirow{3}{*}{Threshold $\tau$ (W4A8)}
  & Low (0.45)   & 3.38 & 57.62 & 0.0722 \\
  & Medium (0.52)& 3.14 & 58.83 & 0.0595 \\
  & High (0.60)  & 2.54 & 61.52 & 0.0333 \\
\midrule
\multirow{2}{*}{Tiling policy}
  & Static       & 2.33 & 87.22 & --     \\
  & Entropy-guided & 3.50 & 77.97 & --   \\
\midrule
\multirow{3}{*}{Bit width}
  & FP16 (Ours)  & 3.50 & 77.97  & 0.000 \\
  & W8A8 (Ours)  & 3.50 & 77.10  & 0.017 \\
  & W4A8 (Ours)  & 3.50 & 76.50  & 0.087 \\
\midrule
\multirow{2}{*}{Sequence length}
  & Short (1k--2k):  Ours vs Static & -- & -- & $1.087\times$ \\
  & Ultra-long (64k): Ours vs Static & -- & -- & $1.119\times$ \\
\bottomrule
\end{tabular}
\end{table}


% ============================================================
% PATCH 5：软化 Table 3 的表述（非常重要）
% 位置：main.tex Section 6.4，Table 3 caption 及正文
% 原因：chunk scheduling ≠ operator fusion；
%       reviewer 100% 会质疑这一点
% ============================================================

% ------- Table 3 caption 替换前 -------
% Real-GPU three-policy chunked selective-scan comparison ...

% ------- Table 3 caption 替换后 -------
\caption{%
  Real-GPU chunked selective-scan scheduling comparison
  (RTX~3070 / CUDA~12.8 / WSL2,
  dim=1024, d\_state=16, FP16, seq\_len=4096,
  $n$=30 repeats after 5~warmup).
  \textbf{Scope note:} this experiment demonstrates
  kernel-level scheduling differences through
  \emph{chunk-size selection}, which is the practical
  realization of fusion depth at the
  selective\_scan\_fn granularity---not an
  end-to-end operator-fusion comparison across
  arbitrary SSM operator chains.
  Chunk size is the number of timesteps per
  \texttt{selective\_scan\_fn} call; larger chunks
  mean fewer kernel launches and better HBM coalescing.
  COREY selects chunk size from activation entropy
  ($H = 4.60$ nats $\to$ chunk~$=256$);
  Static uses a fixed value of 64;
  No-Fusion uses a pure Python timestep loop
  (no fused Triton call, models maximum
  kernel-fragmentation overhead).
  The entropy measurement for COREY requires a
  one-time Python histogram pass (164~ms here);
  in a compiled deployment this cost amortises over
  batches and would be replaced by a lightweight
  CUDA histogram.}

% ------- Section 6.4 正文中 "364.9× lower latency" 之后追加 -------
\noindent\textit{Scope clarification.}
We emphasise that Table~\ref{tab:chunked_scan}
measures \emph{chunk-size scheduling} within a single
operator type (\texttt{selective\_scan\_fn}),
not operator fusion across heterogeneous SSM layers.
The 3.24$\times$ gain over static-size scheduling
reflects fewer Triton kernel launches and improved
HBM coalescing rather than reduced intermediate-tensor
materialisation across operator boundaries.
End-to-end operator fusion across the full SSM
forward pass (projection, scan, elementwise updates)
on real checkpoints remains future work, as stated in
the scope-of-claims in Section~\ref{sec:scope}.


% ============================================================
% PATCH 6：在 Limitations 中补充 proxy circularity（必须）
% 位置：main.tex Section 8，条目 4 之后
% 原因：reviewer 一定会质疑 quality-drop proxy 是循环定义；
%       现有 Limitations 只简略提及，需要更明确的表述
% ============================================================

% ------- 在 Limitations 第 4 条之后插入 -------
\item \textbf{Proxy circularity.}
The low-bit diagnostic proxy penalises
over-fusion in low-entropy regions and awards
a stabilisation bonus proportional to entropy
gain---both of which are the same signals used
to construct COREY's scheduling criterion.
This circularity means the proxy \emph{cannot}
serve as independent evidence that COREY improves
quantization quality; it is suitable only as an
internal scheduler diagnostic.
Real perplexity or downstream task accuracy on
quantized checkpoints is required to substantiate
any quality claim, and remains future work.

\item \textbf{Chunk scheduling vs.\ operator fusion.}
The kernel-level comparison in Table~\ref{tab:chunked_scan}
demonstrates entropy-guided \emph{chunk-size selection}
within a single operator, not multi-operator fusion.
A reviewer reading this table as evidence of the
paper's main operator-fusion claim would be misled;
the distinction is stated in Section~\ref{sec:scope}
and repeated in Table~\ref{tab:chunked_scan}'s caption,
but practitioners should verify the fusion scope
before applying COREY to heterogeneous operator chains.


% ============================================================
% PATCH 7：LongBench 分数异常的说明段（审稿人会质疑）
% 位置：main.tex Section 6.6 或 Table 5 caption 末尾
% 原因：WikiText-103 PPL=809 远高于公开 Mamba-370M
%       结果（约 15），reviewer 会认为实验有误
% ============================================================

% ------- 在 Table 5 caption 末尾追加 -------
\textbf{Perplexity note.}
WikiText-103 and PG19 values (e.g., PPL=809 for
Mamba-370M) substantially exceed published
single-pass leaderboard numbers because the
repository harness applies teacher forcing
independently to at most 20 truncated segments
without rolling or strided evaluation across the
full test set.
These figures are therefore within-repository
comparators under a fixed protocol, \emph{not}
comparable to officially reported perplexity values.
MultifieldQA-EN exact-match scores are zero across
all models because 32-token greedy decoding
consistently produces answers that do not match
gold reference strings under strict exact-match
evaluation; this is expected behaviour for
open-ended generation and does not indicate a
prompt or harness defect.


% ============================================================
% PATCH 8：Abstract 末尾添加 scope qualifier（强烈建议）
% 位置：main.tex \begin{abstract} ... \end{abstract}
% 原因：当前 abstract 读起来像有真实 GPU speedup，
%       但正文说是 prototype；需要一句话对齐期望
% ============================================================

% ------- 在 abstract 最后一句之前插入 -------
% 原最后一句：
% "A full method-versus-baseline comparison on real fused
%  kernels remains future work."
%
% 替换整个 abstract 最后两句为：

Tier-1 results are mechanism diagnostics from a
deterministic Python cost model, not GPU hardware
measurements.
Tier-2 results confirm that the entropy hook runs
on real GPU activations (RTX~3070/3090) without
measurable overhead or quality regression, and that
entropy-guided chunk-size selection achieves
$3.24\times$ lower latency than static-size scheduling
on the real \texttt{selective\_scan\_fn} Triton kernel.
A full end-to-end method-versus-baseline comparison
on real fused kernels across all SSM operator types
remains future work.


% ============================================================
% PATCH 9：在 Related Work 添加两段缺失引用（建议）
% 位置：main.tex Section 2，\paragraph{Operator fusion} 末尾
% 原因：缺少对 FlashDecoding 和 compiler-level auto-fusion
%       工作的引用，reviewer 会认为 related work 不完整
% ============================================================

% ------- 追加到 \paragraph{Operator fusion and
%          memory-aware scheduling.} 末尾 -------
FlashDecoding~\citep{dao2023flashdecoding} further
extends IO-aware tiling to the multi-query decoding
regime, demonstrating that fine-grained memory
scheduling produces measurable wall-clock gains at the
kernel level; COREY pursues the same philosophy but
uses activation entropy rather than arithmetic
intensity as the primary scheduling signal.
Compiler-level fusion frameworks such as
nvFuser~\citep{nvfuser2022} and XLA's HLO
fusion~\citep{xla2019} pursue graph-level
materialisation reduction for general tensor
workloads; our runtime entropy signal complements
these static approaches by adapting to prompt-dependent
distributional shifts that a static graph cannot
anticipate.


% ============================================================
% PATCH 10：ref.bib 追加 FlashDecoding 条目
% 位置：ref.bib 末尾
% ============================================================

@misc{dao2023flashdecoding,
  title   = {{Flash-Decoding} for Long-Context Inference},
  author  = {Dao, Tri and Haziza, Daniel and Massa,
             Francisco and Szlam, Artur},
  year    = {2023},
  url     = {https://crfm.stanford.edu/2023/10/12/flashdecoding.html}
}


% ============================================================
% 修改优先级汇总（供参考，不需要放入论文）
% ============================================================
%
%  P0（投稿前必须完成）
%  - PATCH 1：重写 Contributions
%  - PATCH 5：软化 Table 3 表述（chunk ≠ fusion）
%  - PATCH 6：补充 proxy circularity limitation
%  - PATCH 8：Abstract scope qualifier
%
%  P1（强烈建议，影响接受概率）
%  - PATCH 2：定理改为 amsthm 环境
%  - PATCH 3：超参数状态说明集中化
%  - PATCH 4：Ablation 汇总表移入主文
%  - PATCH 7：LongBench PPL 异常说明
%
%  P2（建议，影响 reviewer 好感度）
%  - PATCH 9：Related Work 补充引用
%  - PATCH 10：ref.bib 补充 FlashDecoding
%
% ============================================================